Replication on multicore considering hierarchy and characteristics of the network

### 2013-02-21 paper.tex
Couple of changes

\paragraph{What problem are you solving, and why is it hard?}
\begin{description}
\item[placement] machine dependent
\item[consistency] need to consider machine \emph{characteristics};
  multicores are \emph{different} from classical distributed systems.
\item[machine characteristics] diverse, fast changing
\end{description}

\paragraph{What's the related work?} People do replication to deal
with scalability challenges on multicores, e.g.\
databases~\cite{Salomie2011, Wiesmann2000} and operating
systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.

\paragraph{What new idea(s) will solve the problems?} Consider machine
characteristics and keep in mind, that multicore machines are
different.

\paragraph{How will you go about it?} Replicas on NUMA domains, show
that overall throughput is higher. Use a quorum based approach for
consistency. Consistency by doing a hierarchical group communication
approach instead of sequential send from same nodes.

\paragraph{How will you know and show it works?} Database?
Microbenchmark? Compare to primary backup, which is typically used.

>>>>

\paragraph{What problem are you solving, and why is it hard?} Three problems:
\begin{description}
\item[placement] machine dependent
\item[consistency] need to consider machine \emph{characteristics};
  multicores are \emph{different} from classical distributed systems.
\item[machine characteristics] diverse, fast changing, complex
\end{description}

\paragraph{What's the related work?} People do replication to deal
with scalability challenges on multicores, e.g.\
databases~\cite{Salomie2011, Wiesmann2000} and operating
systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
don't to it properly. They do not consider machine characteristics.

\paragraph{What new idea(s) will solve the problems?} Consider machine
characteristics and keep in mind, that multicore machines are
different. \\
{\footnotesize Example: sequential consistency on shared memory, do
  not really need to have primary backup.}

\paragraph{How will you go about it?} Replicas on NUMA domains, show
that overall throughput is higher. Then, use a quorum based approach for
consistency. Consistency by doing a hierarchical group communication
approach instead of sequential send from same nodes.

\paragraph{How will you know and show it works?} Database?
Microbenchmark? Compare to primary backup, which is typically
used. Measure time required to apply an update.
